### 2020-06-04 writeup/intro.tex
intro wip

Our main result is to develop tight concentration bounds for the bias and variance of the multi-task estimator for two tasks.
Since the sample size has increased, the variance of the multi-task estimator is \textit{always smaller} than the variance of the single-task estimator.
In Lemma \ref{lem_cov_shift_informal}, we provide a sharp analysis of the reduced variance that scales only with sample size and covariate shift.
Since task models are different, the bias of the multi-task estimator is \textit{always larger} than the bias of the single-task estimator (which is $0$).
Hence, the bias-variance tradeoff determines whether we observe positive or negative transfer.
Using Lemma \ref{lem_cov_shift_informal}, we analyze the bias-variance tradeoff for two tasks in Theorem \ref{thm_main_informal} and extend the analysis to many tasks with same features in Theorem \ref{thm_many_tasks}.
%For the setting of two tasks, we show how the variance of the multi-task estimator  scales with sample size and covariate shift in the following result.
%\textit{Our first contribution} is to develop a concentration bound that arises naturally from the bias-variance tradeoff of $\hat{\beta}_t^{\MTL}$ for two tasks.
%Let $\hat{\beta}_t^{\STL}$ denote the single-task estimator.
%Without loss of generality, let the $t$-th task denote the target task.
%Importantly, the target task's data size is a fixed constant times $p$ in the high-dimensional setting.
%Hence adding more labeled data can help improve its test performance.
%$B\in\real^{p\times r}$
%$\set{W_i \in \real^{r}}_{i=1}^t$

\begin{figure}[!t]
	\begin{subfigure}[b]{0.32\textwidth}
		\centering
		\includegraphics[width=0.98\textwidth]{figures/model_shift_phase_transition.pdf}
		\vspace{-0.075in}
		\caption{Task similarity}
		\label{fig_model_shift}
	\end{subfigure}\hfill
	\begin{subfigure}[b]{0.32\textwidth}
		\centering
		\includegraphics[width=0.98\textwidth]{figures/datapoints_phase_transition.pdf}
		\vspace{-0.075in}
		\caption{Sample size}
		\label{fig_size}
	\end{subfigure}\hfill
	\begin{subfigure}[b]{0.32\textwidth}
		\centering
		\includegraphics[width=0.98\textwidth]{figures/complementary.pdf}
		\vspace{-0.075in}
		\caption{Covariate shift}
		\label{fig_covariate}
	\end{subfigure}
	\caption{%Three takeaways of our theory in Section \ref{sec_insight}.
	We observe that MTL performance
	(a) transitions from pos. to neg. transfer as \textit{task model distance} increases;
	(b) transitions from pos. to neg. transfer as source/target \text{sample ratio} increases;
	(c) worsens as \textit{covariate shift} gets more severe (larger $\lambda$) and source/target \textit{sample ratio} increases -- tasks have the same model here.
	The $y$-axis measures the loss of STL minus MTL.
	}
	\label{fig_model_shift_phasetrans}
	\vspace{-0.3in}
\end{figure}

>>>>

Our main result is to develop tight bounds for the bias and variance of the multi-task estimator for two tasks.
Since the total sample size has increased, the variance of the multi-task estimator is \textit{always smaller} than that of the single-task estimator.
Since task models are different, the bias of the multi-task estimator is \textit{always larger} than that of the single-task estimator (which is $0$ since $n_1 > p$).
Hence, the tradeoff between bias and variance determines whether the transfer is positive or negative.
In Lemma \ref{lem_cov_shift_informal}, we provide a sharp analysis of the variance that scales only with sample size and covariate shift and extend it to the bias.
Combined together, we analyze the bias-variance tradeoff for two tasks in Theorem \ref{thm_main_informal} and extend the analysis to many tasks with same features in Theorem \ref{thm_many_tasks}.
%For the setting of two tasks, we show how the variance of the multi-task estimator  scales with sample size and covariate shift in the following result.
%\textit{Our first contribution} is to develop a concentration bound that arises naturally from the bias-variance tradeoff of $\hat{\beta}_t^{\MTL}$ for two tasks.
%Let $\hat{\beta}_t^{\STL}$ denote the single-task estimator.
%Without loss of generality, let the $t$-th task denote the target task.
%Importantly, the target task's data size is a fixed constant times $p$ in the high-dimensional setting.
%Hence adding more labeled data can help improve its test performance.
%$B\in\real^{p\times r}$
%$\set{W_i \in \real^{r}}_{i=1}^t$

\begin{figure}[!t]
	\begin{subfigure}[b]{0.32\textwidth}
		\centering
		\includegraphics[width=0.98\textwidth]{figures/model_shift_phase_transition.pdf}
		\vspace{-0.075in}
		\caption{Task similarity}
		\label{fig_model_shift}
	\end{subfigure}\hfill
	\begin{subfigure}[b]{0.32\textwidth}
		\centering
		\includegraphics[width=0.98\textwidth]{figures/datapoints_phase_transition.pdf}
		\vspace{-0.075in}
		\caption{Sample size}
		\label{fig_size}
	\end{subfigure}\hfill
	\begin{subfigure}[b]{0.32\textwidth}
		\centering
		\includegraphics[width=0.98\textwidth]{figures/complementary.pdf}
		\vspace{-0.075in}
		\caption{Covariate shift}
		\label{fig_covariate}
	\end{subfigure}
	\caption{%Three takeaways of our theory in Section \ref{sec_insight}.
	We observe a transition from positive to negative transfer as (a) \textit{task model distance} increases and (b) source/target \textit{sample ratio} increases.
	For the special case of having the same task model, we observe in (c) that as source/target \textit{sample ratio} increases, having \textit{covariate shift} worsens the performance of MTL.
	The $y$-axis measures the loss of STL minus MTL.}
	\label{fig_model_shift_phasetrans}
	\vspace{-0.3in}
\end{figure}
